# Day 12 Assigment
# Nama : Isnan El Sady
# Data Science Batch 7

```{r}
# Load library 
library(tidyverse)
library(ggplot2)
library(dplyr)
```

```{r}
# Load Dataset Ames House 
ames = read.csv('D:/Data_Science/Snakes/CSV/train.csv')
```

```{r}
# Ames House dataset glimpse
glimpse(ames)

```

# Question 1 
# Count and visualize one categorical feature of dataset.
# Choosing GarageType variable from dataset
```{r}
ames %>%
  drop_na(GarageType) %>%
  ggplot(aes(fct_rev(fct_infreq(GarageType)))) +
  geom_bar(fill =  '#218bf0' ) +
  coord_flip() +
  labs(x = 'Houses Garage Types Available', y = 'Sum', title = 'Houses Garages Types Count In Ames', subtitle = 'How Many Types of Garage Availabe in Ames Housing?') +
  theme_minimal()
```
# Insight 
# There are 6 six different types of garage available in Ames Housing, with the Attached type having the most count, followed by Dettached type in second and Built-in type in third. 

# Question 2
# Distribution of one continous feature
# CHoosing Overall COnd vaariable of dataset
```{r}
ames %>%
  drop_na(OverallCond) %>%
  ggplot(aes(OverallCond)) +
  geom_histogram(fill =  '#2aab55', binwidth = 1) +
  labs(x = 'Houses Overall Condition (higher is better)', y = 'Sum', title = 'Histogram of Houses Overall Condition', subtitle = 'How is the distribution of Houses Overall Condition in Ames Housing?') +
  theme_minimal()
```
# Insight 
# Most houses condition in Ames fall in to the average region, indexed by 5. WIth an astounding count of 800 houses,

# Question 3
# Visualize both one categorical feature and continous feature
# Choosing Sale Condition adn SalePrice variables
```{r}
ames %>%
  drop_na(SaleCondition,SalePrice) %>%
  ggplot(aes(y = SalePrice, fill = SaleCondition)) +
  geom_boxplot(outlier.shape = 8, outlier.size = 2,outlier.color = 'red') +
  labs(x = NULL, y = 'Sum', title = 'BoxPlot of Houses Sale Price grouped by Houses Sale Condition', subtitle = 'How is the Houses Sale Price when compared based on Houses Sale Condition?') +
  theme_minimal()
```
# Insight 
# Price most houses sold in normal condition are much lower than that of houses sold in partial condiiton. However, some houses sold in normal are sold in a much much larger  price tag. This indicates that perhaps some of that house have a very very goood overall condition.

# Question 4
# Visualize two continous feature 
# Choosing SalePrice and OverallQuality variables.
```{r}
mycolors = c('#e30a38','#e705ee','#f7ef08','#27caca','#d415ea','#0db7f7')
ames %>%
  drop_na(OverallQual,SalePrice) %>%
  ggplot(aes(x = SalePrice, y = OverallQual)) +
  geom_point(color = 'brown', size = 3) +
  labs(x = 'Houses Sale Price', y = 'Houses Overall Quality', title = 'Scatterplot of Houses Sale Price over Houses Overall Quality', subtitle = 'How is the Houses Sale Price when compared based on Houses Quality?') +
  theme_minimal()
```
# Insight
# A higher number of houses quality mostly results in higher price tag. However, there are some houses in encellent quality (indexed by 10) which have a lower price tag several houses. Perhaps it is because the house is indeed in excellent but have a significantly very small area m2.
